---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%")
  
# library(dplyr)
# library(leaflet)
# library(NigeriaDisasterRisks)

data("my_dataset")

adm1_data <- my_dataset$adm1_data

adm2_data <- my_dataset$adm2_data

```

# NigeriaDisasterRisks

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of NigeriaDisasterRisks application is to visualize findings from Nigeria disaster risks layers from various geo-spatial data sources

## Installation

You can install the development version of NigeriaDisasterRisks like so:

``` r
# To install the Nigeria application 

remotes::install_github("szhaider/NigeriaDisasterRisks")

# To launch the app locally
library(NigeriaDisasterRisks)
NigeriaDisasterRisks::run_app()

#To run directly from Github
library(shiny)
shiny::runGitHub("NigeriaDisasterRisks", "szhaider")

```

These are some basic details about the data used in the application:

## Various Disaster Risks dimensions covered

```{r Dimensions, echo=FALSE}
unique(adm2_data$description)

```

## Admin 1 for Nigeria

```{r Admin1, echo=FALSE}
unique(adm1_data$ADM1_NAME)

```
